How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-31 paper.tex
more text

The first step is to read the error message carefully, if there is one; this
obviously doesn't apply in all cases, but it's often applicable and far too
often skipped. It's true that many software packages have cryptic unhelpful
error messages, but far too often people write for help when the solution is
right in front of them. If the error message says ``Could not open file
foo.dat'', it's worth checking whether there is a file called ``foo.dat'' and if
not figuring out what was supposed to create it.

The second step is to check the manual. This might seem trivially obvious, but
you'd be astonished how many emails developers get that are directly answered in
the manual. If the manual is short, you can read the whole thing. If it's
longer, search for relevant-seeming keywords, scan the sections that seem to
pertain to your error message. If there's an FAQ (frequently asked questions)
list, check that first; asking an FAQ, especially in a public forum, is likely
to lead to grumbling.

Next, search the internet for the error message; this works very well for
software with thousands of users, where it might very well deserve to be the
first option. It is less effective with less common packages, but it's an easy
thing to check, so you'd be foolish to skip it.

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
Dr. Tod D. Romo reviewed the document for style and content. Dr. Justin A.
Lemkul made numerous helpful suggestions, particularly regarding language
accessibility. Dr. David H. Mathews provided several editorial suggestions.

>>>>

The first step is to read the error message carefully, if there is one; this
obviously doesn't apply in all cases, but it's often applicable and far too
often skipped. It's true that many software packages have cryptic or unhelpful
error messages, but far too often people write for help when the solution is
right in front of them. If the error message says ``Could not open file
foo.dat'', it's worth checking whether there is a file called ``foo.dat'' and if
not figuring out what was supposed to create it.

The second step is to check the manual. This too might seem trivially obvious,
but you'd be astonished how many emails developers get that are directly
answered in the manual. If the manual is short, you can read the whole thing. If
it's longer, search for relevant-seeming keywords, scan the sections that seem
to pertain to your error message. If there's an FAQ (frequently asked questions)
list, check that first; asking an FAQ, especially in a public forum, is likely
to lead to grumbling.

Next, search the internet for the error message; this works very well for
software with thousands of users, where it might very well deserve to be the
first option. It is less effective with less common packages, but it's an easy
thing to check, so you'd be foolish to skip it.  Search for the whole text of
the error (excluding any verbiage that looks like it depends on the compiler,
etc), with and without the package name. The latter can be important in the case
where the problem isn't with the package per se, but with something else in your
setup.

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
Dr. Tod D. Romo reviewed the document for style and content. Dr. Justin A.
Lemkul made numerous helpful suggestions, particularly regarding language
accessibility. Dr. David H. Mathews provided several editorial suggestions. Dr.
Jeffrey Lewis had suggestions regarding searching for help.
